A generalized definition of multidimensional item response theory parameters

### 2024-06-19 output/paper_draft/paper_M2PLM_parameters.Rmd
Moves "test space" conclusions to "Results"
This commit separates the "invariance" condition of the model from the results regarding the test space, which are moved to a new section in the results. In this new section, some properties of the test space are also explained.

### Test space and latent space

@@

We shall refer to this new space $`r TEST_SPACE`$ as
the *test space* [@zhang_theoretical_1999].
Although the inverse relationship between their respective inner product
Gram matrices induces a bijective relationship between the two sets of spaces,
it is worth highlighting that test space $`r TEST_SPACE`$
and latent space $`r LATENT_SPACE`$ are different entities. Only in the
orthonormal case the two spaces share a common inner product
(i.e., the dot product), and thus can be mistaken.

@@

\begin{equation}
  `r SLOPE_MAX_PARAM_EQ`.                                     (\#eq:slope-param)
\end{equation}

@@

Applying Proposition 2, if $`r ANGLE_VEC_TS_ITEM`$ is
the vector of direction angles of $`r DISCR_VECTOR`$,
in the test space $`r TEST_SPACE`$ we get

@@

with $`r DIAG_MATRIX_INNER_PROD_INV`$ a diagonal matrix where
$`r MATRIX_INNER_PROD_INV_EL_DIAG_EQ`$.

@@

The item location $`r MIL_PARAM`$ is defined as the distance and direction
from the origin to the point of maximum slope [@reckase_difficulty_1985].
By analogy with the unidimensional case, $`r MDISC_SYM`$ is defined as
$4 `r SLOPE_MAX_PARAM`$ [@reckase_discriminating_1991].
Therefore, we may define the $`r MIL_PARAM`$ and $`r MDISC_SYM`$ using
equations \@ref(eq:distance-param) through \@ref(eq:dir-cos-vec-test-space).
However, as they depend on the inner product matrix $`r INNER_PROD_MATRIX`$,
the choice we make of this matrix will lead us to different definitions of
the parameters.

>>>>

### Item response function invariance

@@

@@

\begin{equation}
  `r SLOPE_MAX_PARAM_EQ`,                                     (\#eq:slope-param)
\end{equation}

@@

## Test space vs. latent space

Before presenting the results about the parameters,
we must make a few remarks regarding the vector space $`r TEST_SPACE`$.
As shown before, this space is an entity by itself,
distinct from the latent space $`r LATENT_SPACE`$.
Despite this, the dot product in the exponent of Equation
\@ref(eq:eq:M2PL-formulation) induces a bijective relationship between
their two sets of respective bases.
Explicitly, if $`r TRAIT_VECTOR`$ is represented in basis $`r LS_BASIS`$
with inner product gram matrix $`r INNER_PROD_MATRIX`$,
$`r DISCR_VECTOR`$ is represented in basis $`r TEST_SPACE_BASIS`$
with inner product gram matrix $`r INNER_PROD_MATRIX_INV`$,
for any pair of bases $`r LS_BASIS`$ and $`r TEST_SPACE_BASIS`$.
Only when the two bases are orthonormal,
the two spaces share a common inner product (i.e., the dot product),
and thus can be mistaken.
However, it is worth noting that, although their representation
can be superimposed in this case,
they are still two different spaces. <!-- # TODO: To discussion? -->
Following @zhang_theoretical_1999, we shall refer to space $`r TEST_SPACE`$ as
the test space, as it is the space where
the items (i.e., the test elements) are represented.

We must make a few remarks here.
First, the transformation to the orthonormal bases of the two spaces allows
mapping the $`r MODEL_ACRONYM`$ parameters indistinctly in the two spaces,
by projecting one space onto the other.
This allows representing the coordinates of the discrimination vectors
in the latent space and, conversely,
the coordinates of the latent trait vectors in the test space.
As we can see, the invariance of the model holds,
no matter in which space we represent the coordinates.
<!-- # TODO: Incluir la condición de invarianza de las coordenadas en los dos espacios (Foto pizarra)? -->
Second, and most importantly, if the test space is
where the item parameters naturally lie, they must be represented in this space,
and not in the latent space.
Therefore, we may find the direction angles of $`r DISCR_VECTOR`$
in the test space.
If $`r ANGLE_VEC_TS_ITEM`$ is
the vector of direction angles of $`r DISCR_VECTOR`$,
applying Proposition 2
in the test space $`r TEST_SPACE`$ we get

@@

with $`r DIAG_MATRIX_INNER_PROD_INV`$ a diagonal matrix where
$`r MATRIX_INNER_PROD_INV_EL_DIAG_EQ`$.
<!-- # TODO: Revisar esto bien. Esto sólo aplica correctamente si efectivamente
"equiparamos" las bases U y U*. Además, en la Proposición 2 estamos asumiendo
que la "base de enlace" es la canónica, no una base ortonormal cualquiera. -->
As we will see later, this representation is very convenient, as
the alignment of the item vectors with the coordinate axes has a direct,
meaningful interpretation.

@@

The item location $`r MIL_PARAM`$ is defined as the distance and direction
from the origin to the point of maximum slope [@reckase_difficulty_1985].
By analogy with the unidimensional case, $`r MDISC_SYM`$ is defined as
$4 `r SLOPE_MAX_PARAM`$ [@reckase_discriminating_1991].
Therefore, we may define the $`r MIL_PARAM`$ and $`r MDISC_SYM`$ using
Equations \@ref(eq:distance-param) through \@ref(eq:dir-cos-vec-test-space).
However, as they depend on the inner product matrix $`r INNER_PROD_MATRIX`$,
the choice we make of this matrix will lead us to different definitions of
the parameters.
